To be FAIR: Theory Specification Needs an Update

### 2025-03-02 manuscript.Rmd
Add lange reference, closes #63

In sum, while it is impossible to communicate a theory completely unambiguously,
scholars should strive to reduce unnecessary ambiguity to the greatest possible extent.
<!-- Accessibility requires theoreticians to explicit as possible about assumptions and ontological definitions to eliminate unnecessary ambiguity. -->
<!-- At the same time, it is important to recognize that there is an upper bound on interpretability, which means that it is impossible to eliminate all ambiguity. -->
It may benefit scientific discourse to normalize explicit ambiguity (these are things we don't know yet) and anticipate misunderstanding,
to invite others to fill in the blanks and motivate ever further explication of theory.
A theory's Accessibility is increased by
reducing dependencies on (implicit) background knowledge,
explication of assumptions,
formalization,
and explicit cross-references to relevant resources such as papers, ontologies, macro-theories, measurement instruments, experimental designs [REF LANGE CHECKLIST].

>>>>

In sum, while it is impossible to communicate a theory completely unambiguously,
scholars should strive to reduce unnecessary ambiguity to the greatest possible extent.
<!-- Accessibility requires theoreticians to explicit as possible about assumptions and ontological definitions to eliminate unnecessary ambiguity. -->
<!-- At the same time, it is important to recognize that there is an upper bound on interpretability, which means that it is impossible to eliminate all ambiguity. -->
It may benefit scientific discourse to normalize explicit ambiguity (these are things we don't know yet) and anticipate misunderstanding,
to invite others to fill in the blanks and motivate ever further explication of theory.
A theory's Accessibility is increased by
reducing dependencies on (implicit) background knowledge,
explication of assumptions,
formalization,
and explicit cross-references to relevant resources such as papers, ontologies, macro-theories, measurement instruments, experimental designs [@langeChecklistIncentivizingFacilitating2025a].
